### 2018-04-20 manuscript.tex
another small rewording to introduce first expls

Fist, we install the \texttt{rethomics} packages (see the webpage for installation instructions) and download the data to extract the zip archive in our working directory.
Then, we load the necessary \texttt{rethomics} packages:

>>>>

Fist, we install the \texttt{rethomics} packages (see the webpage for installation instructions), download the zip archive containing the raw data and extract all files into our working directory.
Then, we load the necessary \texttt{rethomics} packages:
